---
title: "sumcat_analysis"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{sumcat_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
\section*{Introduction}

\section*{Functions}

\section*{Analysis}
We begin our analysis by first installing our package `sumcat` into your R session.
```{r setup}
library(sumcat)
```

We can then load the `water_potability` data set that we will be running our analysis on along with `water_test` data set.

```{r}
data("water_potability")
data("water_test")
```

After loading these data sets into our R session, we need to set a seed to allow for reproducibility, allowing the user to follow along with this example. As well as, that we will be making the models for our analysis using the `model_cat()` function. We are interested in a starting point for this categorical analysis so our `formula` statement for the function will be our response variable `Potability` with all of our explanatory variables.

```{r}
set.seed(121521)
model <- model_cat(Potability ~ ., water_potability, water_test)
```

We can view our model statements by using the package `summary` function to display these results.

```{r}
summary(model)

```

We can then see how the predictive power, by seeing how the accuracy compares among the four models: logistic regression, random forest, support vector machines, and linear discriminant analysis. This is done by calling the `rank` function which shows a dataframe of the models and accuracies.

```{r}
rank_methods(model)
```











